### 2020-01-14 overview.tex
added 2 figures in num methods.

Using discrete marker points to specify and track particle motions, front-tracking methods constitute an intuitive description of finite-size particles and have been used in multiphase flow simulations since the inception of digital computers \citep{Daly1969, unverdi_tryggvason_1992a, tryggvason_bunner_esmaeeli_juric_al-rawahi_tauber_han_nas_jan_2001a}. [add more] \quad
The general methodology is to (i) prescribe the particle location by distributing a set of Lagrangian points on the particle surface, (ii) advect them using the local flow velocity, and (iii) compute the extra forces at the updated particle position.
In the case of liquid droplets, (ii) and (iii) can be written as
\begin{equation}
 \begin{aligned}
   \frac{d \bm{X}_i}{dt} = \bm{u}(\bm{X}_i),
 \end{aligned}
\end{equation}
\begin{equation} \label{eq:surf-tension}
 \begin{aligned}
   \bm{f} = \gamma \kappa \bm{n} \delta (\bm{X}_i) ,
 \end{aligned}
\end{equation}
where $\bm{X}_i$, $i=1,2,\dots,N_L$ denote the positions of the Lagrangian points, $\bm u$ the local flow velocity, $\bm f$ the forcing term, $\gamma$ the surface tension coefficient, $\kappa$ the interface curvature, $\bm n$ the interface normal vector, and $\delta$ the Dirac delta function. Eq.\ \eqref{eq:surf-tension} correspoinds to the internal boundary conditions due to surface tension, cf.\ Eq.\ \eqref{eq:stress-bc}. No-slip boundary conditions on solid particles can be represented in similar ways and will be described momentarily.

Despite the conceptual simplicity, there are several technical details that require careful treatment in a numerical simulation.
First, due to deformation of the particle or non-uniformity of the flow field, the Lagrangian particles may need to be redistributed, added, or deleted to ensure numerical stabilty and accuracy.
This may be particularly cumbersome when droplets coalesce or breakup.
Second, advection of the marker points requires interpolation of the velocity field.
Third, the internal boundary conditions are to be computed on the fluid mesh, thus a ``spreading'' procedure is nessesary to couple the particle influence back. This is usually done with smeared delta function, such as that of \cite{Peskin}.

We explain these in details below for a special class of front-tracking methods.

@@

First we describe three Eulerian methods.
marker functions, boundary conditions (surface tension) \citep{Brackbill_JCP_1992}
Also ghost fluid method.

@@

\iffalse
steps:
\begin{enumerate}
\item reconstruct the interface from the local volume fraction. (not required by algebraic VOF)
\item advect the interface.
\end{enumerate}
\fi

@@

Geometrically, the normal and the curvature of the interface can be readily derived from the level set as below,\footnote{Some authors express the curvature as $\kappa = -\nabla \cdot {\bm n}$, cf.\ \cite{Desjardins_JCP_2008, ICLS}. This is due to different sign conventions and care should be taken in using the curvature value.}
\begin{subequations}
 \begin{equation}
    {\bm n} = \frac{\nabla \phi}{\abs{ \nabla \phi }},
 \end{equation}
 \begin{equation} \label{eq:curv}
    \kappa = \nabla \cdot {\bm n}.
 \end{equation}
\end{subequations}

>>>>

Using discrete marker points to specify and track particle motions, front-tracking type-of methods are perhaps the most intuitive approach for modelling finite-size particles and have been used in multiphase flow simulations since the inception of super computers \citep{Daly1969, Peskin, Glimm_1982, unverdi_tryggvason_1992a, tryggvason_bunner_esmaeeli_juric_al-rawahi_tauber_han_nas_jan_2001a, Pozrikidis_JCP2001, Muradoglu_Tryggvason_2014}.
The general methodology is to
(i) prescribe the particle location by distributing a set of Lagrangian points on the particle surface (see Figure \ref{fig:front-track}),
(ii) advect them using the local flow velocity, and
(iii) update the fluid properties and compute the extra forces at the updated particle position.
In the case of liquid droplets, (ii) and (iii) can be written as
\begin{equation}
 \begin{aligned}
   \frac{d \bm{X}_i}{dt} = \bm{u}(\bm{X}_i),
 \end{aligned}
\end{equation}
\begin{equation} \label{eq:surf-tension}
 \begin{aligned}
   \bm{f} = \gamma \kappa \bm{n} \delta (\bm{X}_i) ,
 \end{aligned}
\end{equation}
where $\bm{X}_i$, $i=1,2,\dots,N_L$ denote the positions of the Lagrangian points, $\bm u$ the local flow velocity, $\bm f$ the forcing term, $\gamma$ the surface tension coefficient, $\kappa$ the interface curvature, $\bm n$ the interface normal vector, and $\delta$ the Dirac delta function. Eq.\ \eqref{eq:surf-tension} correspoinds to the normal stress jump condition due to surface tension, cf.\ Eq.\ \eqref{eq:stress-bc}. No-slip boundary conditions on solid particles can be represented in similar ways as will be described momentarily.

Despite the conceptual simplicity, there are several technical details that require careful treatment in a numerical simulation.
First, due to deformation of the particle or non-uniformity of the flow field, the Lagrangian particles may need to be redistributed, added, or deleted from time to time to ensure numerical stabilty and accuracy.
This is particularly cumbersome when droplets coalesce or breakup.
Second, advection of the marker points requires interpolation of the velocity field, as the moving grid is generally non-aligned with the background fixed mesh.
Third, the internal boundary conditions (no-slip or surface tension) are to be computed on the fixed mesh, thus a ``spreading'' procedure is nessesary to couple the particle and fluid dynamics. This is usually done with smeared delta function. Now we explain these in more details under a specific class of front-tracking methods.

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.6\columnwidth]{marker-points.pdf}
  \caption{Marker points on a triangular droplet.}
  \label{fig:front-track}
\end{figure}

@@

First we describe three Eulerian methods.
marker functions, boundary conditions (surface tension) \citep{Brackbill_JCP_1992}
Also ghost fluid method.
Figure \ref{fig:front-capture}.

\begin{figure}%[t]
  \centering
  \includegraphics[width=\columnwidth]{front-capture-comp.pdf}
  \caption{Comparison of the three front-capturing methods for a 1D droplet of radius 0.5, centered at $x=1.033$. Markers indicate the nodal values of the representative functions. Dashed lines depict the boundary of the droplet.
  (upper) The volume-of-fluid representation, where $C=1$ inside the droplet.
  (middle) The level set representation, where $\phi >0$ outside the droplet.
  (lower) The phase field representation, where the profile is given by $c=0.5[1-\mathrm{tanh}(\phi/\epsilon)]$, with $\epsilon=0.1$.}
  \label{fig:front-capture}
\end{figure}

@@

@@

Geometrically, the normal and the curvature of the interface can be readily derived from the level set as below,\footnote{Some authors express the curvature as $\kappa = -\nabla \cdot {\bm n}$, cf.\ \cite{Desjardins_JCP_2008, ICLS}. This is merely due to different sign conventions for the level set.}
\begin{subequations}
 \begin{equation}
    {\bm n} = \frac{\nabla \phi}{\abs{ \nabla \phi }},
 \end{equation}
 \begin{equation} \label{eq:curv}
    \kappa = \nabla \cdot {\bm n}.
 \end{equation}
\end{subequations}
